j_play

### 2020-11-28 scripts/draft_play.Rmd
Hid table code so it doesn't kill your computers

#Table
apa_table(
  count_by_year,
  digits = 0,
  caption = "Headcount by Classification and District, Select Years 1996-2020",
  note = "Number of students is estimated and does not include masked data.",
  col.names = c("School Year",
                "Special Needs Description",
                "Number of Students")
)

#Table is huge - pivot_wider by year and maybe select specific years to look at

>>>>

#Table
#apa_table(
#  count_by_year,
#  digits = 0,
#  caption = "Headcount by Classification and District, Select Years 1996-2020",
#  note = "Number of students is estimated and does not include masked data.",
#  col.names = c("School Year",
#                "Special Needs Description",
#                "Number of Students")
#)

#Table is huuuge - do not run table code yet or your computer will be frozen for 5 minutes.
